How predictable is extinction?

### 2018-11-01 doc/gsa2018_talk.tex
various typographic/font size changes
updated plots with seth comments

\begin{frame}
  \frametitle{Data being analyzed}

  \begin{columns}
    \begin{column}{0.5\textwidth}
      \includegraphics[width=\textwidth,height=0.8\textheight,keepaspectratio=true]{../results/figure/occ_time_label}
    \end{column}
    \begin{column}{0.5\textwidth}
      \includegraphics[width=\textwidth,height=0.8\textheight,keepaspectratio=true]{../results/figure/age_label}
    \end{column}
  \end{columns}

@@

  \begin{itemize}%[<+->]
    \item Encoding the past
      \begin{itemize}
        \item Change in geographic range between current observation and previous observation.
        \item Average global temperature at time of previous observation (Mg/Ca isotope).
        \item Age in millions of years at time of observation.
      \end{itemize}
    %\item \alert{Compare} models using WAIC/LOOIC.
    \item Explore model adequacy using posterior predictive distribution.
    \item Estimate out-of-sample predictive performance using \(k\)-fold cross-validation.
  \end{itemize}

@@

  \includegraphics[width=\textwidth,height=0.8\textheight,keepaspectratio=true]{../results/figure/auc_hist}

@@

  \includegraphics[width=\textwidth,height=0.8\textheight,keepaspectratio=true]{../results/figure/auc_ts}

@@

  \includegraphics[width=\textwidth,height=0.8\textheight,keepaspectratio=true]{../results/figure/fold_auc}

@@

  \includegraphics[width=\textwidth,height=0.8\textheight,keepaspectratio=true]{../results/figure/fold_auc_time}

@@

  \begin{itemize}
    \item \alert{The past matters\dots} 
      \begin{itemize}
        \item Our best supported model includes our historical covariates and allows all effects to vary over time.
      \end{itemize}
    \item \alert{But not that much\dots}
      \begin{itemize}
        \item None of our models are good at predicting extinction.
      \end{itemize}
    \item Perhaps mechanisms behind changes to geographic range operate at sub-million year scales. Perhaps their effects are weak/masked at million (or greater) year scales.
  \end{itemize}

@@

\begin{frame}
  \frametitle{Acknowledgements}
  \begin{columns}
    \begin{column}{0.5\textwidth}
      \begin{itemize}
        \item \textbf{Seth Finnegan}
        \item Adiel Klompmaker 
        \item Emily Orzechowski
        \item Larry Taylor
        \item Sara Kahanamoku
        \item Josh Zimmt
        \item Franziska Franeck \\(University of Oslo)
      \end{itemize}
    \end{column}
    \begin{column}{0.5\textwidth}
      \begin{center}
        \includegraphics[height=0.15\textheight,width=\textwidth,keepaspectratio=true]{figure/github-logo}

@@

        @PeterDSmits
      \end{center}
      \vspace*{0.02\textheight}
      \begin{center}
        \includegraphics[height=0.25\textheight,width=\textwidth,keepaspectratio=true]{figure/INAlogo}
      \end{center}
    \end{column}
  \end{columns}
\end{frame}

>>>>

\begin{frame}
  \frametitle{Data being analyzed: Neptune database}

  \begin{columns}
    \begin{column}{0.1\textwidth}
      \begin{center}
        \includegraphics[width=\textwidth,height=0.15\textheight,keepaspectratio=true]{figure/calc}

        \includegraphics[width=\textwidth,height=0.15\textheight,keepaspectratio=true]{figure/dino}

        \includegraphics[width=\textwidth,height=0.15\textheight,keepaspectratio=true]{figure/foram}

        \includegraphics[width=\textwidth,height=0.15\textheight,keepaspectratio=true]{figure/rad}

        \attrib{\footnotesize{UCL}}
      \end{center}
    \end{column}
    \begin{column}{0.4\textwidth}
      \includegraphics[width=\textwidth,height=0.8\textheight,keepaspectratio=true]{../results/figure/occ_time_label}
    \end{column}
    \begin{column}{0.4\textwidth}
      \includegraphics[width=\textwidth,height=0.8\textheight,keepaspectratio=true]{../results/figure/age_label}
    \end{column}
  \end{columns}

  \footnotesize{Global occurrences from Deep Sea Drilling Program and Ocean Drilling Project. -- Lazarus. 1994. Math. Geo.; Spencer-Cervato. 1999. Palaeo. Elec.}

@@

  \begin{itemize}%[<+->]
    \item Encoding the past
      \begin{itemize}
        \item Change in geographic range between current observation and previous observation.
        \item Average global temperature at time of previous observation (Mg/Ca elemental ratio).
        \item Age in millions of years at time of observation.
      \end{itemize}
    %\item \alert{Compare} models using WAIC/LOOIC.
    \item Explore model adequacy using posterior predictive distribution.
    \item Estimate out-of-sample predictive performance using \(k\)-fold cross-validation.
  \end{itemize}

@@

  \begin{center}
    \includegraphics[width=\textwidth,height=0.8\textheight,keepaspectratio=true]{../results/figure/auc_hist_zoom}

    \footnotesize{AUC = 0.7-0.8 acceptable/fair}
  \end{center}

  \begin{center}
    \includegraphics[width=\textwidth,height=0.8\textheight,keepaspectratio=true]{../results/figure/auc_hist}

    \footnotesize{AUC = 0.7-0.8 acceptable/fair}
  \end{center}

@@

  \begin{center}
    \includegraphics[width=\textwidth,height=0.8\textheight,keepaspectratio=true]{../results/figure/auc_ts}
  \end{center}

@@

  \begin{center}
    \includegraphics[width=\textwidth,height=0.8\textheight,keepaspectratio=true]{../results/figure/fold_auc_zoom}

    \footnotesize{AUC = 0.7-0.8 acceptable/fair}
  \end{center}

@@

  \begin{center}
    \includegraphics[width=\textwidth,height=0.8\textheight,keepaspectratio=true]{../results/figure/fold_auc_time}
  \end{center}

@@

  \begin{itemize}
    \item \alert{The past matters\dots} 
      \begin{itemize}
        \item Our best supported model includes our historical covariates and allows all effects to vary over time.
      \end{itemize}
    \item \alert{But not that much\dots}
      \begin{itemize}
        \item Models only average/fair expected out-of-sample performance.
      \end{itemize}
    \item Mechanisms behind changes to geographic range operate at sub-million year scales. Perhaps their effects are weak/masked at million (or greater) year scales.
  \end{itemize}

@@

\begin{frame}
  \frametitle{Acknowledgements}
  \begin{columns}
    \begin{column}{0.5\textwidth}
      \begin{itemize}
        \item UC Berkeley
          \begin{itemize}
            \item Adiel Klompmaker 
            \item Emily Orzechowski
            \item Larry Taylor
            \item Sara Kahanamoku
            \item Josh Zimmt
          \end{itemize}
        \item University of Oslo
          \begin{itemize}
            \item Franziska Franeck
          \end{itemize}
        \item Neptune DB/MFN - Berlin
          \begin{itemize}
            \item David Lazarus
          \end{itemize}
      \end{itemize}
    \end{column}
    \begin{column}{0.5\textwidth}
      \begin{center}
        \includegraphics[height=0.15\textheight,width=\textwidth,keepaspectratio=true]{figure/github-logo}

@@

        @PeterDSmits
      \end{center}

      \vspace*{0.02\textheight}

      \begin{center}
        \includegraphics[height=0.25\textheight,width=\textwidth,keepaspectratio=true]{figure/nsb_logo}
      \end{center}
    \end{column}
  \end{columns}
\end{frame}
